\section{Comparison against Timelines}

In our project outline, we set specific timelines to complete certain tasks, such as conducting Exploratory Data Analysis (EDA) and evaluating the performance of different models.

We promised to complete the EDA by March 8th, and we were able to achieve that goal. We analyzed the SNLI dataset in depth and provided insights into its characteristics, including data visualization. We also discussed the preprocessing requirements for the SNLI dataset and provided code to preprocess the dataset.

Moreover, we implemented Logistic Regression, Bidirectional LSTM, etc. models for the SNLI dataset and compared the performance with each other. By accomplishing these tasks according to the project timeline, we were able to stay on track and ensure timely delivery of project objectives.


\section{Work plan till final submission}

The further plan is to

\begin{itemize}
	\item Research different NLI datasets and select a few for analysis. Preprocess and clean the selected datasets by removing stop words, stemming/lemmatization, and removing any unnecessary columns. Conduct exploratory data analysis (EDA) on the cleaned datasets to identify any patterns, trends, and anomalies.
	\item Evaluate the performance of the baseline model (Logistic Regression) and compare it with other models after experimenting with different models like Gated recurrent units (GRUs), different layers with LSTMs.
	\item Explore different embeddings like Word2Vec, GloVe, and FastText. Implement these embeddings in the BiLSTM model and evaluate their performance.
	\item Research and study the state-of-the-art models like BERT and RoBERTa. Implement BERT on the selected dataset and fine-tune its hyperparameters to improve its performance.
	\item Compare the performance of BERT with the previously selected models.
\end{itemize}
